EvoSuite at the SBST 2015 Tool Competition

### 2015-02-22 papers/sbst15/paper_sbst15.tex
minor paper editing

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved TODO line
coverage,TODO branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and TODO mutation score. On average, \EVOSUITE
produced TODO tests per class, and it took an average of TODO per class to
do so.
% (with \EVOSUITE configured to 3 minutes per class).

@@

For the other four classes with 0\% coverage, \EVOSUITE failed to
generate any tests for other reasons. For \<CharMatcher>, the issue is
an issue in how \EVOSUITE handled timeouts, which resulted in
\EVOSUITE's master process killing the client process before tests
were written to disk. For \<CycleHandler> and \<WikipediaInfo>,
\EVOSUITE ran into an issue when trying to resolve the generic type
parameters of some dependency classes; this also affects \<Page> with
1.49\% coverage. This issue could be avoided by omitting generic type
parameters, as the Java compiler would only issue warnings about such
missing parameters. However, as \EVOSUITE is aiming to produce
readable tests, we feel it is important to properly handle Java
Generics. Finally, for \<Response> the constructor requires a
parameter of type \<java.net.HttpURLConnection>, which is an abstract
class without concrete subclasses. As \EVOSUITE does not produce stubs
automatically, it therefore failed to instantiate \<Response> objects.

>>>>

The results of \EVOSUITE on the benchmark classes are listed in
Table~\ref{table:results}. On average, \EVOSUITE achieved 55.36\% line
coverage, 47.19\% branch coverage\footnote{Using Cobertura's definition
  of branch coverage, which only counts conditional statements, not
  edges in the CFG.}, and 41.02\% mutation score. 
%On average, \EVOSUITE
%produced TODO tests per class, and it took an average of TODO per class to
%do so.
% (with \EVOSUITE configured to 3 minutes per class).
On average, \EVOSUITE took 6 minutes and 11 seconds per class to generate test cases. 
The generated test suites take on average 2.1 seconds to run per class.

@@

For the other four classes with 0\% coverage, \EVOSUITE failed to
generate any tests for other reasons. For \<CharMatcher>, there was 
an issue in how \EVOSUITE handled timeouts, which resulted in
\EVOSUITE's master process killing the client process before tests
were written to disk. For \<CycleHandler> and \<WikipediaInfo>,
\EVOSUITE ran into an issue when trying to resolve the generic type
parameters of some dependency classes; this also affects \<Page> with
1.49\% coverage. This issue could be avoided by omitting generic type
parameters, as the Java compiler would only issue warnings about such
missing parameters. However, as \EVOSUITE is aiming to produce
readable tests, we feel it is important to properly handle Java
Generics. Finally, for \<Response> the constructor requires a
parameter of type \<java.net.HttpURLConnection>, which is an abstract
class without concrete subclasses. As \EVOSUITE does not produce stubs
automatically, it therefore failed to instantiate \<Response> objects.
